---
title: "Simple document"
author: Joie Li
date: 2024-09-10
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r import_packages, echo = FALSE, message = FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
# if echo = FALSE, only shows output
# if eval = FALSE, only shows code

samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Learning assessment
```{r learning_assessment_1, message = FALSE}
df = tibble(sample = rnorm(500), 
            pos = sample > 0,
            abs_val = abs(sample))

ggplot(df, aes(x = abs_val)) + geom_histogram()
```
The median of this data frame is `r round(median(df$abs_val), 2)`

# Formatting text
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_

**bold**  or  __bold__

`code`

superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell